A Fast Unified Model for Parsing and Sentence Understanding

### 2016-04-01 writing/hard_stack_paper/paper.tex
Fig 3 updates. (Had to shift legend to a weird place to prevent too much figure-shrinking)

\begin{figure}
\centering
\resizebox{0.85\linewidth}{!}{
\begin{tikzpicture} 
\begin{axis}[xmin=0, ymin=0, xlabel=Batch size, ylabel=Feedforward time (sec),
             xtick={0,256,512,1024,2048}, legend style={at={(1.1, 0.98)},anchor=north east}]
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU \citep{irsoy2014deep}}
  \addplot table [x={Batch size}, y=RNN, col sep=tab] {runtime.csv};
  \addlegendentry{RNN}
\end{axis}
\end{tikzpicture}
}
\caption{Feedforward speed comparison.}
\label{fig:speed}
\end{figure}

>>>>

\begin{figure}
\centering
\resizebox{0.85\linewidth}{!}{
\begin{tikzpicture}
\begin{axis}[xmin=0, ymin=0, xlabel=Batch size, ylabel=Feedforward time (sec),
             xticklabels={0,32,64,128,256,512,1024,2048}, xmode=log, log basis x=2,
             legend style={at={(0.55, 0.5)},anchor=north west}]
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU \citep{irsoy2014deep}}
  \addplot table [x={Batch size}, y=RNN, col sep=tab] {runtime.csv};
  \addlegendentry{RNN}
\end{axis}
\end{tikzpicture}
}
\caption{Feedforward speed comparison.}
\label{fig:speed}
\end{figure}
